### 2021-05-12 shared/analysis.tex
WIP : Pdf

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

\begin{document}
	\begin{figure}
		\begin{minted}{python}

@@

	klee_dump(path_prob)
	klee_dump(sum) // E[heads in "n" runs] 
		\end{minted}
		\caption{Program listing for $n$ bernoulli trails experiment.}
	\end{figure}

@@

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.
\end{document}

>>>>

\documentclass[usenames,dvipsnames,acmsmall]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[nounderscore]{syntax}
\usepackage{bussproofs}
\usepackage{mathtools}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{minted}

\begin{document}
	\begin{figure}
		\begin{minted}{python}
		def count_heads(prob : float, n : int):
			x = 0
			while(n > 0):
				d = bernoulli.rvs(size=1, p=prob)[0]
				x = x + d
				n = n - 1
			return x
		\end{minted}
	\caption{Program to $count$ heads over $n$ bernoulli trials.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}
		if (prob <= 0.5) E(x) < 0.4 * n else E(x) >= 0.6 * n
		\end{minted}
	\caption{\texttt{Assert} we want to check for failure.}
	\end{figure}
	\begin{figure}
		\begin{minted}{python}

@@

	klee_dump(path_prob)
	klee_dump(sum) // E[heads in "n" runs] 
		\end{minted}
		\caption{Program listing for $n$ bernoulli trails experiment with transformation for \texttt{KLEE}.}
	\end{figure}

@@

\begin{equation}	
	w_1 = \prod_{j=1}^{10} choice\_prob_{1}(j) ,
	\quad
	sum_1 = \sum_{j=1}^{10} components(\vec{d_1}) ,
\end{equation}
\begin{equation}	
	w_2 = \prod_{j=1}^{10} choice\_prob_{2}(j) ,
	\quad
	sum_2 = \sum_{j=1}^{10} components(\vec{d_2}) ,
\end{equation}
\begin{equation}	
	w_3 = \prod_{j=1}^{10} choice\_prob_{3}(j) ,
	\quad
	sum_3 = \sum_{j=1}^{10} components(\vec{d_3}) ,
\end{equation}
\begin{equation}	
	w_4 = \prod_{j=1}^{10} choice\_prob_{4}(j) ,
	\quad
	sum_4 = \sum_{j=1}^{10} components(\vec{d_4}) ,
\end{equation}
\begin{equation}	
	w_5 = \prod_{j=1}^{10} choice\_prob_{5}(j) ,
	\quad
	sum_5 = \sum_{j=1}^{10} components(\vec{d_5}) ,
\end{equation}
\begin{equation}
	\vec{d_1} \neq \vec{d_2} \neq \vec{d_3} \neq \vec{d_4} \neq \vec{d_5}
\end{equation}
\begin{equation}
	EV(heads) = (\sum_{i=1}^{k}{w_i * sum_i}),
\end{equation}
\begin{equation}
	\enspace
	EV(heads) = (w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
\begin{equation}
	\enspace
	Objective_2 = maximize(w_1 * sum_1 \enspace + \enspace w_2 * sum_2 \enspace + \enspace w_3 * sum_3 \enspace + \enspace w_4 * sum_4 \enspace + \enspace w_5 * sum_5)
\end{equation}
Statistically, maximizing $Objective_1$ must also maximize $Objective_2$ and thus we make the query $maximize(\sum_{i=1}^{k}{w_i})$ to the optimizing solver finally.

\begin{figure}
	\centering
	\includegraphics[scale=0.15]{abstract.pdf}
	\caption{Multiple $random$ paths corresponding to different $\vec{d}$'s but a single $abstract$ path.}
\end{figure}

\begin{figure}
	\begin{minted}{python}
	prob = 0.435, n = 8 (8 coin flips), k = 240 (randomized paths)
	prob = 0.551, n = 5 (5 coin flips), k = 27 (randomized paths) 
	\end{minted}
	\caption{Values for \texttt{Assert} failure.}
\end{figure}
\end{document}
